Spatial Reasoning and Statistical Graphics

### 2014-11-03 Paper/Draft1/TestingVisualAptitude.Rnw
Add libraries for string manipulation, chaining

library(reshape2)
suppressMessages(library(ggplot2))
library(plyr)
library(grid)
suppressMessages(library(gridExtra))
library(xtable)
source(paste(codedir, "Analysis.R", sep=""))

>>>>

library(reshape2)
suppressMessages(library(ggplot2))
library(plyr)
library(grid)
suppressMessages(library(gridExtra))
library(xtable)
library(stringr)
library(magrittr)
source(paste(codedir, "Analysis.R", sep=""))
